---
title: "feasible-fishing outcomes"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(dplyr)
library(ggplot2)
theme_set(theme_bw())
```


```{r}

targets::tar_load("all", store = here::here("_targets"))

```


## Hill 1

```{r}

hill1 <- filter(all, var == "hill1")

ggplot(hill1, aes(p)) + 
  geom_histogram(bins = 100) +
  geom_vline(xintercept = .05)

mean(hill1$p < .05)

```

In nearly all instances (of those sampled) the distribution of hill numbers for the fs differs from for the logseries. 



Note I am not sure if Hill numbers are directly comparable over variation in S and N. 

```{r}

ggplot(hill1, aes(S, N, color = loc_diff, shape = loc_diff < 0)) +
  geom_point() +
  scale_color_viridis_c(option = "plasma") +
  scale_x_log10() +
  scale_y_log10() +
  geom_point(data = filter(hill1, p > .05), color = "black") 

ggplot(hill1, aes(N/S, loc_diff, color = S)) +
  geom_point()

```

There's a line where the difference goes from positive to negative. For high N/S, the difference tends to be less than 0 (logseries has lower values than the feasible set). For low N/S, the difference tends to be greater than 0 (logseries has higher values than the feasible set). 



```{r}

ggplot(hill1, aes(loc_diff)) +
  geom_histogram()

```

There's a gap in these data in N/S. 


## Hill 2

```{r}

hill2 <- filter(all, var == "hill2")

ggplot(hill2, aes(p)) + 
  geom_histogram(bins = 100) +
  geom_vline(xintercept = .05)

mean(hill2$p < .05)

```

In nearly all instances (of those sampled) the distribution of hill numbers for the fs differs from for the logseries. 



Note I am not sure if Hill numbers are directly comparable over variation in S and N. 

```{r}

ggplot(hill2, aes(S, N, color = loc_diff, shape = loc_diff < 0)) +
  geom_point() +
  scale_color_viridis_c(option = "plasma") +
  scale_x_log10() +
  scale_y_log10() +
  geom_point(data = filter(hill2, p > .05), color = "black") 

```

There's a line where the difference goes from positive to negative. For high N/S, the difference tends to be less than 0 (logseries has lower values than the feasible set). For low N/S, the difference tends to be greater than 0 (logseries has higher values than the feasible set). 



```{r}

ggplot(hill2, aes(loc_diff)) +
  geom_histogram()

```



## Comparison to v

```{r}

ggplot(hill1, aes(J, v, color = loc_diff, shape = loc_diff < 0)) +
  geom_point() +
  scale_x_log10() +
  scale_color_viridis_c(option = "plasma")


```


## Comparison to theta

```{r}

hill1 <- hill1 %>%
  mutate(theta =   2 * v * J)

ggplot(hill1, aes(theta, loc_diff)) +
  geom_point()


```